Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-24 Arxiv/main.tex
update dirichlet theorem

% \author[*]{Jiawen Liu}
% \author[**]{Mark Bun}
% \author[*]{Gian Pietro Farina}
% \author[*]{Marco Gaboardi}
% \affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
% \affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}

\begin{abstract} Bayesian inference is a statistical method which
allows one to derive a \emph{posterior} distribution,
starting from a \emph{prior} distribution and observed data. Several
approaches have been explored in order to make this process differentially
private. For example, \cite{dimitrakakis2014robust}, and
\cite{wang2015privacy} proved that, under specific conditions, sampling from
the posterior distribution is already differentially private. \cite{zhang2016differential}, \cite{foulds2016theory},
designed differentially private mechanisms that output a
representation of the full posterior distribution.

@@

\maketitle

@@

 \begin{thm}
 \label{thm_hellinegr_equality}
 for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
  $$
  \alpha_2 = \beta_1, \alpha_1 = \beta_2, \alpha_0 + \alpha_1 = \beta_0 + \beta_2 \alpha_0 + \alpha_2 = \beta_0 + \beta_1.
  $$
 \end{thm}

 \begin{thm}
 \label{thm_candidate_divide}
 there are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either 
 $$
 = 2\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big )
 $$ or 
 $$
 =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r].
 $$
 \end{thm}
 % proportional too $\hellinger(\bysinfer(\dataobs),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r']$. 
 \begin{proof} of Theorem \ref{thm_candidate_divide}.

 We assume the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e. $u(z,\dataobs) = u(r,\dataobs)$ is $|z|$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.

 From Theorem \ref{thm_hellinegr_equality}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.

 The same way in Dirichlet-multinomial system. By combination and permutation, $|z|$ can take value of 1 or 3 or 6 in 3 dimensionality, and trivially in higher dimensions.
 \end{proof}

@@

\begin{proof}
Based on Theorem \ref{thm_hellinegr_equality} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.

>>>>

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
\begin{abstract} Bayesian inference is a statistical method which
allows one to derive a \emph{posterior} distribution,
starting from a \emph{prior} distribution and observed data. Several
approaches have been explored in order to make this process differentially
private. For example, \cite{dimitrakakis2014robust}, and
\cite{wang2015privacy} proved that, under specific conditions, sampling from
the posterior distribution is already differentially private. \cite{zhang2016differential}, \cite{foulds2016theory},
designed differentially private mechanisms that output a
representation of the full posterior distribution.

@@

@@

 \begin{thm}
 \label{thm_hellinegr_equality_beta}
 for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
  $$
  \alpha_2 = \beta_1, \alpha_1 = \beta_2, \alpha_0 + \alpha_1 = \beta_0 + \beta_2 \alpha_0 + \alpha_2 = \beta_0 + \beta_1.
  $$
 \end{thm}

\begin{thm}
 \label{thm_hellinegr_equality_dirichlet}
 In Dirichlet-multinomial system, for 3 different Dirichlet distributions $\dirichlet(\valpha)$, $\dirichlet(\vbeta_1)$ and $\dirichlet(\vbeta_2)$, $\hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_1)) = \hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_2))$ iff:
  $$
  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2).
  $$
 \end{thm}

 \begin{thm}
 \label{thm_candidate_divide}
 There are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either 
 $$
 = 2\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big )
 $$ or 
 $$
 =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r].
 $$
 \end{thm}
 \begin{proof} of Theorem \ref{thm_candidate_divide}.

 Let $|z|$ be the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e. $u(z,\dataobs) = u(r,\dataobs)$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.

 From Theorem \ref{thm_hellinegr_equality_beta}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
 \end{proof}

\begin{thm}
 \label{thm_candidate_divide_dirichlet}
 In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
 $$
 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
 = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
 $$ 
 and $|z| = \min\{\frac{k!}{a_1! a_2! \cdots a_{k_a}!},\frac{k!}{b_1! b_2! \cdots b_{k_b}!}\}$, where $\sum{a_i} = \sum{b_i} = k$.
 \end{thm}

 \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.
 By 
 \end{proof}

@@

\begin{proof}
Based on Theorem \ref{thm_hellinegr_equality_beta} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.
